Notes on Semi-Supervised `Novelty Detection'

### 2011-04-11 semisupervised/notes.tex
Some  more fixes

\subsection{What does a ROC curve looks like for an optimal detector}
\note{The ROC curve shape shows if a detector is perfect given an input space.
      (Or at least I think so (though I haven't write any proof)).
      I guess somewhere there should be literature reference to such a simple concept}

@@

This leads to the important property:

whatever threshold function you use,
if you get a convex ROC curve, there is no way to perform better using that input space.

@@

The system objective was to detect novel data from a given known set of 6 categories.
Two tests where run:
\begin{enumerate}
\item Using perfect knowledge of the probability functions both thresholds where compared for performance (\autoref{tab:dora-data-perfect}).
\item The models described in \autoref{sec:dora-models} were used to learn the probability functions and the thresholds were compared (\autoref{tab:dora-data-simple}).
\end{enumerate}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{dora-data/roc-perfect.pdf}
\caption{\label{tab:dora-data-perfect}ROC curve for thresholds based on perfect information running on the dora distribution}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{dora-data/roc-simple.pdf}
\caption{\label{tab:dora-data-simple}ROC curve for thresholds learned on samples from samples in the dora distribution}
\end{figure}

>>>>

\subsection{What does a ROC curve looks like for an optimal detector}
\note{The ROC curve shape shows if a detector is perfect given an input space.
      I guess somewhere there should be literature reference to such a simple concept}

@@

This leads to the important property:
\emph{whatever threshold function you use,
if you get a convex ROC curve, there is no way to perform better using that input space.}

@@

The system objective was to detect novel data from a given known set of 6 categories.
Two tests where run:
\begin{enumerate}
\item Using perfect knowledge of the probability functions both thresholds where compared for performance (\autoref{fig:dora-data-perfect}).
\item The models described in \autoref{sec:dora-models} were used to learn the probability functions and the thresholds were compared (\autoref{fig:dora-data-simple}).
\end{enumerate}

@@

As possible to see in \autoref{fig:dora-data-perfect} if we are able to use the unlabelled data to build a correct $P(x)$ then we obtain an optimal detector.

\autoref{fig:dora-data-simple} shows how close our solution approaches the optimal by using creating models to for the conditional and unconditional probability from samples.

Important to notice that our model of unconditional probability is very simple, it assumes semantic data to be independent from each other.

\note{Describe better which approach we used to model $P(G)/P(G')$}
\note{Perform experience with real data}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{dora-data/roc-perfect.pdf}
\caption{ROC curve for thresholds based on perfect information running on the dora distribution}
\label{fig:dora-data-perfect}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{dora-data/roc-simple.pdf}
\caption{ROC curve for thresholds learned on samples from samples in the dora distribution}
\label{fig:dora-data-simple}
\end{figure}
